final_project_draft

### 2022-04-04 draft.Rmd
April 4th graded after class commit. Worked with theme() in ggplot.

ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
  geom_point() +
  labs(x = " ", 
       y = " ",
       title = "Top 25 Highest Political Donations by NFL Team Owners in 2016",
       colour = "Political Party",
       subtitle = "What Influence Could NFL Team Owners Have on Elections?") +
  scale_colour_viridis_d() +
  theme_bw()
```

@@

kable(owner_rank2, caption = "Who Makes the Most Donations Across All Leagues?",
      col.names = c("Owner", "Team", "League", "Amount of Donations Made")) %>%
  kable_classic()
```

@@

ggplot(data = frequent, aes(x = amount, y = Owner, label = Amount, colour = Party)) +
  geom_point() +
  labs(title = "How Much Do They Donate?",
       y = "Owners",
       x = "Amount Donated",
       colour = "Party") +
  scale_colour_brewer(palette = "Dark2") +
  theme(legend.position = "bottom")

@@

ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
  geom_col() +
  coord_flip() +
  scale_fill_viridis_d() +
  labs(title = "Count of Donations by Political Party?",
       x = "Political Party",
       y = "Count") +
  theme(legend.position = "bottom") +
  geom_label(data = cj_party, aes(label = n), show.legend = FALSE) 
```

>>>>

ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
  geom_point() +
  labs(x = " ", 
       y = " ",
       title = "How Much Did NFL Owners Donate in 2016?",
       colour = "Political Party",
       subtitle = "What Influence Could NFL Team Owners Have on Elections?") +
  scale_colour_viridis_d() +
  theme_bw() +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 9.5),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 8),
        legend.title = element_text(family = "mono",
                                    face = "bold",
                                    size = 8),
        legend.text = element_text(family = "mono",
                                   size = 8),
        axis.text = element_text(family = "mono",
                                 size = 8),
        legend.box.background = element_rect())
```

@@

kable(owner_rank2, caption = "<b>Who Makes the Most Donations Across All Leagues?<b>", format = "html",
      col.names = c("Owner", "Team", "League", "Donations Made")) %>%
  kable_styling(html_font = "Cambria", bootstrap_options = "striped",
                font_size = 9) 
```

@@

ggplot(data = frequent, aes(x = amount, y = Owner, label = Amount, colour = Party)) +
  geom_point() +
  labs(title = "How Many Donations Have They Made?",
       subtitle = "Examining The Monetary Amount of Observed Political Donations",
       y = " ",
       x = " ",
       colour = "Party") +
  scale_colour_brewer(palette = "Dark2") +
    theme_bw() +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 12),
        axis.text.x = element_text(family = "mono"),
        axis.text.y = element_text(family = "mono"),
        legend.title = element_text(family = "mono", 
                                    face = "bold",
                                    size = 5),
        legend.text = element_text(family = "mono",
                                   size = 5),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 9),
        legend.box.background = element_rect())

@@

ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
  geom_col() +
  coord_flip() +
  scale_fill_viridis_d() +
  labs(title = "Count of Donations by Political Party?",
       x = " ",
       y = " ") +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono")) +
  geom_label(data = cj_party, aes(label = n), show.legend = FALSE) 
```
